Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
All images, updated

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS.png}
% \todo{Show Comparison between Geant4 and MCNPX calculations}
    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCNPX calculations~\cite{Prokofiev14}}
    \label{fig:MCComparison}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
	\label{fig:TOFFrameOverlapspectrum}}\\
	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
	\label{fig:SUP10FrameOverlapspectrum}}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}

>>>>

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS}
% \todo{Show Comparison between Geant4 and MCNPX calculations}
    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCNPX calculations~\cite{Prokofiev14}}
    \label{fig:MCComparison}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{CUPTOFtofspectraRADECS.png}}
	\label{fig:TOFFrameOverlapspectrum}}\\
	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUPtofspectraRADECS.png}
	\label{fig:SUP10FrameOverlapspectrum}}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}
